\documentclass[letterpaper]{resume}
\pagenumbering{gobble}

\begin{document}

\author{Mark Piper}
\email{mdpiper@gmail.com}
\phone{303-725-1306}
\webpage{https://mdpiper.github.io}
\streetaddress{3507 Smuggler Way}
\citystatezip{Boulder, CO 80305}

\maketitle


\section{Summary}

\vspace{0.5em}
\noindent 
Research software engineer
with over 18 years of experience
helping people solve
scientific programming, data analysis, and data visualization problems.


\section{Work Experience}

\affiliation[Research Associate]
            {University of Colorado}
            {2013--present}
\begin{compactitem}[\itembullet]
  \item I use open-source software to develop model coupling
    cyberinfrastructure for the NSF-funded Community Surface Dynamics
    Modeling System (CSDMS) within the Institute of Arctic and Alpine
    Research (INSTAAR). My current research interests are in model
    benchmarking and uncertainty quantification in Earth surface
    process models.
\end{compactitem}

\affiliation[Product Manager]
            {Harris Geospatial Solutions
              (formerly Exelis Visual Information Solutions)}
            {2012--2013}
\begin{compactitem}[\itembullet]
  \item I was the product manager and technology evangelist for the
    scientific data analysis and visualization language IDL. I guided
    the overall direction of the product. My responsibilities included
    performing market research and competitive analyses, gathering
    customer feedback, writing user stories, developing requirements,
    and communicating this information effectively to our Engineering
    team.
\end{compactitem}

\affiliation[Solutions Engineer]
            {Harris Geospatial Solutions}
            {2010--2012}
\begin{compactitem}[\itembullet]
  \item I acted as technology evangelist for IDL. I provided external
    support to users through live seminars and webinars, presentations
    at scientific conferences, blogging, and custom programming
    solutions. I provided internal technical product assistance for
    Sales, Marketing, Tech Support, Services, and Product Management.
\end{compactitem}

\affiliation[Professional Services Engineer]
            {Harris Geospatial Solutions}
            {1999-2010}
\begin{compactitem}[\itembullet]
  \item As an instructor, I designed, developed and taught
    introductory through advanced-level programming courses in IDL and
    ENVI. I also created domain-specific courses on signal processing,
    medical image processing, and scientific programming with IDL. As
    a consultant, I worked on customer projects using IDL, ENVI, C,
    Java, and Fortran.
\end{compactitem}


\section{Education}

\affiliation[Ph.D., Astrophysical, Planetary, and Atmospheric Sciences]
            {University of Colorado, Boulder, Colorado}
            {1995--2001}
\affiliation[M.S., Meteorology]
            {Penn State, University Park, Pennsylvania}
            {1992--1994}
\affiliation[B.S., Mathematics]
            {University of Wisconsin, Madison, Wisconsin}
            {1988--1992}


\section{Software technologies}

\vspace{0.5em}
\begin{compactitem}[\itembullet]
  \item Languages: Python, Java, Fortran, IDL, bash, C, MATLAB, Javascript
  \item Tools: Git, CMake, make, Subversion, Eclipse, Emacs
    (preferred), Vim, Slurm, Torque, PBS, ant, Jupyter Notebook,
    Jupyterhub, Markdown, \LaTeX
  \item OS: Linux, macOS, Windows
\end{compactitem}


\section{Professional Associations, Activities, and Awards}

\vspace{0.5em}
\begin{compactitem}[\itembullet]
  \item Member, American Geophysical Union, 2001--present
  \item Member, American Meteorological Society, 1992--present
  \item Pragmatic Product Marketing certification, 2013
  \item University of Colorado Graduate School Fellowship, 1995-1998
  \item Hans Neuberger Award for Outstanding Teaching, 1993
  \item Research Experience for Undergraduates field work in Greenland
    repairing automatic weather stations with Prof. C.R. Stearns,
    Department of Atmospheric and Oceanic Sciences, 1992
\end{compactitem}

\section{Outside Activities}

\vspace{0.5em}
\begin{compactitem}[\itembullet]
  \item TIPS certified server, 2016
  \item Founder and captain of Bighorn, a club ultimate team based in
    Colorado that competes in the 40+ division of USA Ultimate.
\end{compactitem}


\end{document}

%%
%% 
%% Extra words, phrases, etc.
%%
%%

Research software engineer
with over 18 years of experience working with people to solve
scientific programming, data analysis, and visualization problems.

I enjoy helping people solve technical problems.

Thirteen years experience solving -- and communicating with
others how to solve -- scientific programming, data analysis and
visualization problems with IDL and ENVI.

\item As the IDL product owner, translated user feedback to product
  development. Worked with product manager and lead developer to
  prioritize development for future releases of IDL.  Responsible for
  internal and external technical IDL product launch communication.
\item Developed and presented quarterly live seminars and webinars on
  topics ranging from numerical analysis techniques to file formats to
  visualization techniques in IDL.
\item Helped organize and host the 2010 IDL User Group
  meeting. Organized and conducted workshops at this meeting and
  others. Currently planning the 2012 User Group meeting.
\item Attended conferences (e.g., AGU, AMS) to meet customers and
  conduct market research.
\item Created and maintained a blog, The IDL Data Point:
  idldatapoint.com.
\item Created technical content for marketing; applied to brochures
  and the company website.
\item Acted as a resource to the broader IDL user community through
  communication with long-time customers and through involvement with
  the comp.lang.idl-pvwave newsgroup.

  \item Taught introductory through advanced-level programming classes
  in IDL and ENVI, with over 150 classes and 1500 students taught to
  excellent reviews. Responsible for developing and maintaining
  materials for these courses, as well as designing and developing new
  courses.
\item Developed applications with IDL and ENVI. Examples include
  constructing a front-end for a hyperspectral scene simulator in ENVI
  and using IDL to assist NASA in the prediction and mapping of the
  debris path of the Space Shuttle Columbia tragedy.
\item Conducted shoulder-to-shoulder instruction and consulting.
\item Internal resource to tech support, sales, engineering
  and other consultants.
